\bf Enhancing Scheduling Robustness with Task Completion Feedback and Resource Requirement Biasing

### 2019-05-02 paper.tex
Wordsmith description of proportionate bias strategy results and conclusion/future work section.  Use IEEEtran bibstyle

Neither the proportionate nor simple bias strategies achieve acceptible
results with errors as high as $50\%$.  In Figures
\ref{fig:nofeedback-pbias-mederror} and \ref{fig:nofeedback-sbias-mederror}
the effect of proportionate and simple bias strategies are shown, respectively,
in the case of $5\%$ error with no feedback and ideal bias value $P=5\%$.
In the case of Figure \ref{fig:nofeedback-pbias-mederror} and proportionate
bias strategy all four scheduling algorithms complete about one third fewer
workflows at a normalized tardiness of $-0.25$ and below although most of those
workflows are instead completed at normalized tardiness up to $0$, so they are
still completed before their deadline.  CMSA with both cost functions completes
a few more workflows mildly late (normalized tardiness $0.25$ and below), PLLF
completes more workflows at normalized tardinesses up to $1$, and FCFS a few
more at $4+$.  Overall, the proportionate bias strategy fairly effectively
makes all scheduling algorithms robust to errors up to $5\%$ even without any
actual platform feedback available.

@@

The case for why complete and reliable feedback of scheduled task completions
from an actual platform to the model used for scheduling decision-making was
found to be necessary to achieve robust performance of scheduling algorithms,
as first described in previous work \cite{pdpta18}. Furthermore we have
demonstrated the use of partial feedback to be insufficient at achieving
similar robustness, but have proposed the use of biasing the model parameters
to prevent or reduce the likelihood of the model underestimating task
requirements thereby modeling tasks as completing earlier than their actual
completion. Three biasing strategies were proposed, each with different
assumptions of what knowledge is available about the error inherent in the
model and different tradeoffs of balancing the amout of overestimation vs.
likelihood of underestimation of task requirements.  Through simulated case
studies we demonstrated that each biasing strategy is useful for achieving
robustness of scheduling algorithm performance at different amount of model
error.

Future work that remains includes analysis of whether the combination of
partial feedback with any of the biasing strategies can achieve greater
robustness.  Additionally, other biasing strategies or alternatives to
biasing will be explored to increase robustness or address cases where
the amount of error in the model is unknown.  Finally, the use of more
sophisticated approaches such as machine learning may be applied to either
supplement or replace feedback information from the actual platform.

\bibliography{paper}{}
\bibliographystyle{unsrt}

>>>>

Neither the proportionate nor simple bias strategies achieve acceptible
results with errors as high as $50\%$.  In Figures
\ref{fig:nofeedback-pbias-mederror} and \ref{fig:nofeedback-sbias-mederror}
the effect of proportionate and simple bias strategies are shown, respectively,
in the case of $5\%$ error with no feedback and ideal bias value $P=5\%$.
For the proportionate bias strategy, all four scheduling algorithms complete
about one third fewer workflows at a normalized tardiness of $-0.25$ and below
although most of those workflows are completed at normalized tardiness up to
$0$, which is still before their deadline.  CMSA with both cost functions completes
a few more workflows mildly late (normalized tardiness $0.25$ and below), PLLF
completes more workflows at normalized tardinesses up to $1$, and FCFS a few
more at $4+$.  Overall, the proportionate bias strategy fairly effectively
makes all scheduling algorithms robust to errors up to $5\%$ even without any
actual platform feedback available.

@@

The case for why complete and reliable feedback of scheduled task completions
from an actual platform to the model used for scheduling decision-making was
found to be necessary to achieve robust performance of scheduling algorithms,
as first described in previous work \cite{pdpta18}. Furthermore we have
demonstrated the use of partial feedback to be insufficient at achieving
similar robustness, but have proposed the use of biasing the model parameters
to prevent or reduce the likelihood of the model underestimating task
requirements thereby modeling tasks as completing earlier than their actual
completion. Three biasing strategies were proposed with unique trade-offs
of assumed knowledge about error bounds and degree to which they decrease
underestimation and increase overestimation of task requirements. Through
simulated case studies we demonstrated that each biasing strategy is useful
for achieving robustness of scheduling algorithm performance at different
amounts of model error.

Future work may include combination of partial feedback with biasing
strategies.  Additionally, other biasing strategies or alternatives to
biasing will be explored to increase robustness or address cases where
the amount of error in the model is unknown.

\bibliographystyle{IEEEtran}
\bibliography{paper}{}
